---
title: "Assignment 7"
author: "Mabior Ater"
date: "08/11/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r}
library(tidyverse) # QUESTION 2
my_url <- "http://ritsokiguess.site/STAC32/dolphins.csv"
span <- read_csv(my_url)
span
names(span)
span %>% select(mercury,sex)
```
```{r}
span %>% select(matches("^.t$"))
```

## Including Plots

You can also embed plots, for example:

```{r}
span %>% filter(sex == "female")
```
```{r}
span %>% filter(age < 15) -> mean_1
mean_1
mean(mean_1$mercury)
span %>% filter(age > 25) -> mean_2
mean_2
mean(mean_2$mercury)
median(mean_2$mercury)
median(mean_1$mercury)
```
```{r}
ggplot(span, aes(x = sex, y = mercury)) + geom_boxplot()

```
For the graph, it gravitates for a negatively skewed, so it shows on the boxplot of a median closer to the uper quatiles. Hence the data constitute of higher frequencies of low valued scores, and we can recognize this when comparing the mean and median. Median (315) > mean2. 

```{r}
span %>%
  mutate(fs = factor(sex)) %>%
  pivot_longer(age:mercury, names_to="ball", values_to="distance") %>% 
  ggplot(aes(x = ball, y = distance, group = sex, colour = sex)) +
  geom_point() + geom_line()
```

#QUESTION 1
```{r cars}
myurl <- "http://ritsokiguess.site/STAC32/utils.txt"
j_y <- read_delim(myurl," ")
j_y
```



```{r pressure, echo=FALSE}
j_y %>% pivot_longer(`31`:`56`, names_to="old_cols", values_to="values") -> cars 
cars #tidy data attempt
```

```{r}
mytidy <- "http://ritsokiguess.site/STAC32/utils_tidy.csv"
read_csv(mytidy) -> memmk
memmk 
```

```{r}
# graph 
ggplot(memmk, aes(x = memmk$consumption, y = memmk$temperature)) + geom_point() + geom_smooth()
```
*d)* The patterns I see on the graph is a slight upward trend based on the smooth trend but i do see there consist of outliers that are bit too low and high. But, the data shows the trend of upward move, thus detailing the temperature and consumption are positively correlated.
